Enforced Invariant Confluence

### 2018-09-19 doc/paper/sections/merge_reduction.tex
Shrinking paper.
Fixed confluence/closure typo.
From reviewer 12:

> The paper states that in the end of Section 3, "invariant closure is
> completely ignorant of reachability", whereas in Section 5, "invariant
> closure is fundamentally a property of reachability". Which one is
> correct?

Very keen eye by the reviewer! That was a typo. This commit fixes that.

\section{Merge Reduction}\seclabel{MergeReduction}
In \secref{InvariantClosure}, we discussed how \invariantclosure{} is
fundamentally a property of reachability and that \invariantclosure{} is
sufficient but not necessary for \invariantconfluence{} because it fails to
incorporate any notion of reachability. Using this intuition, we established
\thmref{IclosureEquivalentIconfluence} and then exploited the theorem in
\algoref{InteractiveDecisionProcedure}. In this section, we again take
advantage of this intuition to develop a new sufficient condition for
\invariantconfluence{} that can be checked without user interaction and that
covers some cases not covered by \invariantclosure{}.

@@

{\input{figures/merge_reducible}}

>>>>

\section{Merge Reduction}\seclabel{MergeReduction}
In \secref{InvariantClosure}, we discussed how \invariantconfluence{} is
fundamentally a property of reachability and that \invariantclosure{} is
sufficient but not necessary for \invariantconfluence{} because it fails to
incorporate any notion of reachability. Using this intuition, we established
\thmref{IclosureEquivalentIconfluence} and then exploited the theorem in
\algoref{InteractiveDecisionProcedure}. In this section, we again take
advantage of this intuition to develop a new sufficient condition for
\invariantconfluence{} that can be checked without user interaction and that
covers some cases not covered by \invariantclosure{}.

@@

% {\input{figures/merge_reducible}}
